ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-07-12 paper.tex
Added reference abbreviations, minor stylistic change and edits to fit into 11 pages

The system can benefit from future work that focuses on improving the flexibility and usability of the system. 
New datasets that includes the 3D position of objects and camera, similar to what has been done in robotics~\cite{active2017dataset} but with a more diverse set of real scenes, would make it possible to extend our solution training more accurate transition and observation models that can cope with depth.
The usability of the system can potentially be improved by more sophisticated audio interfaces and creating adaptive control algorithms that change the interface's behaviour based on the user performance over time~\cite{gallina2015}.  
%Furthermore, such a dataset will make it possible to replace the relational transition and observation functions used in this work, with more realistic ones that will allow a wider set of actions to be used.

>>>>

The system can benefit from future work that focuses on improving the flexibility and usability of the system. 
New datasets that include the 3D positions of the objects and camera, similar to what has been done in robotics~\cite{active2017dataset} but with a more diverse set of real scenes, would make it possible to train our model with more accurate transition and observation models and possibly extend it to be able to cope with depth.
The usability of the system can potentially be improved with a more sophisticated audio interface and adding adaptive control algorithms that change the interface's behaviour based on the user performance over time~\cite{gallina2015}.  
%Furthermore, such a dataset will make it possible to replace the relational transition and observation functions used in this work, with more realistic ones that will allow a wider set of actions to be used.
